---
title: "Open Canada Data Explorer"
output:
  flexdashboard::flex_dashboard:
  vertical_layout:  scroll # fill # scroll
  orientation: columns # rows
  social: menu
  source_code: embed
runtime: shiny
---


```{r global, include=FALSE}
knitr::opts_chunk$set(echo = F)

if (T) {  
  library(shiny)
  library(shinyBS) # https://stackoverflow.com/questions/33925430/shiny-plot-results-in-popup-window https://stackoverflow.com/questions/61667924/create-a-small-window-to-describe-the-meaning-of-filters-in-shiny
  
  
  
  library(magrittr);   library(ggplot2); 
  # library(dtplyr)
  # library(dplyr)
  
  library(lubridate,  quietly=T); options(lubridate.week.start =  1)
  library(data.table); options(datatable.print.class=TRUE); options(datatable.print.rownames = T)
  # options(datatable.print.nrows = 300) # 100
  options(datatable.print.topn=3) # 5
  
  # library(dygraphs);   
  # library(ggpubr)
  library(DT); library(plotly);   
  
  library(stringr); library(forcats) 
  library(ckanr);   library(cansim)
  
  options(digits = 3)
  # options(max.print = 100) # 1000
  options(scipen = 999) # remove scientific notation
  
  
  
  
  
  dateToday <- format(Sys.time(), '%d %B, %Y') %>% dmy; dateToday
  
  "%wo%" <- function(x, y) setdiff(x,y) 
  # "%ni%" <-  Negate(%in%)
  
  yesno <- c("Yes", "No")
  
  
  # r <- reactiveValues() -----
  
  
  if ( shiny::isRunning() ) {  
    r <- reactiveValues()
  } else {
    r <- list()
  }
  
  reset.reactive <- function() {
    # r$filesOpened = 0
    r$dtAll <- NULL
    r$dt <- NULL
    r$dt0 <- NULL
    r$dt00 <- NULL
    r$filter = NULL
    r$cols = 1
  }
  
  reset.reactive()
  
  
  datatable.title <- function(dt, title=NULL) {
    # https://rstudio.github.io/DT/options.html
    dt %>% DT::datatable (
      filter = "top",  caption = title, rownames=F, extensions =  c('ColReorder', 'Buttons'),
      options = list(
        dom = 'Blfrtip',
        # paging = FALSE, 
        # pageLength=50, scrollX='400px', # horizontal scroll
        scrollX = TRUE,       scrollY = "600px",
        
        colReorder = TRUE,
        # lengthMenu = list(c(10,25,100,-1), c(5,10,25,50,"All")),
        lengthMenu = list(c(10,25,100,-1), c(5,10,25,50,"All")),
        buttons = c('copy', 'csv', 'excel', 'pdf', 'print') 
      ) )
  }
  
  dt.findCategoricalColumns <- function (dt) {
    cols  <- c (dt[, which(sapply(.SD, is.factor))], dt[, which(sapply(.SD, is.character))] );cols
  }
  
  
  
  dt.findColumnsByType <- function (
    dt, is.what=function(x){is.ordered(x) | is.integer(x) | is.character(x)}
  ) {
    cols <- names(dt[sapply(dt, is.what)]); cols
  }
  
  dt.findColumnsByFunctionInNthRow <- function (dt, is.what=function (x) {x>0}, rows_to_use=1) {
    # cols <- names(dt[sapply(dt, is.what)]); cols
    cols  <- dt[rows_to_use, which(sapply(.SD, is.what))];cols
  }
  
  
  dt.convertColumnToOrdered <- function(dt, cols) {
    # for (col in cols) dt[, (col) := ordered(dt[[col]])] #fastest
    # or 
    dt[, (cols):=lapply(.SD, ordered), .SDcols=cols]
    # dt[, cols] <- lapply(dt[, cols, with = FALSE], ordered)
  }
}

```



# Make selection {.sidebar}



```{r UI: select.data_source select.data_address}

popify(
  # tipify(
  selectInput(
    "select.data_source",  "Select data source:",  width="100%",
    choices = c( 
      
      "Statistics Canada" = "statcan",
      "Ontario open data" = "ontario",
      "URL"= "url",
      "Hard drive" = "local",
      "Upload "= "upload")
  ),
  title = "Tip:",
  content = "You can open local file by providing its full name",
  placement = "right", trigger = "hover"
  #   content = paste0("1) Read from hard drive (working directory only)\n 2) Upload from hard drive (small file only)")
  # )
)



renderUI({ 
  req(input$select.data_source)
  switch (
    input$select.data_source,
    
    "local" = {   
      aFiles <- list.files(path=".", pattern=".csv", all.files=FALSE,    full.names=FALSE) # pattern = "^[a-lr]",
      # paste0("Select a .csv file from your working (", getwd(), ") directory"),
      tipify(
        selectInput ("select.data_address", paste0("Select a file"), choices = aFiles,  width="100%",
                     selected = aFiles[1]
                     # "NEXUS-PIK Session Details 2020706 2020920.csv-10-10.csv"
        ),
        "Tip: If you don't see your file, change working directory")
    } ,
    
    "url" = 
      textInput ("select.data_address", paste0("Type URL ") ),
    
    
    
    "upload" = 
      tipify(
        fileInput("select.data_address", h6("Choose CSV file:"), multiple = F, accept = c("text/csv", "text/comma-separated-values,text/plain", ".csv")),
        "Only small files (less than 1 Mb) cane be uploaded"), 
    
    "statcan" = 
      textInput("select.data_address",  
                # tags$a(href="https://www150.statcan.gc.ca/n1/en/type/data", "Enter StatCan Table number. If you don't know it, click on this link to search for it", target="_blank"),
                "Enter StatCan Table number:", # (Leave blank to search by keyword):",
                "13-10-0768-01", width="100%"),
    
    "ontario" = 
      textInput("select.data_address",  
                "Enter Ontario Table number: ",  "97622ce6-c06a-4970-afe5-be540c748f24", width="100%") # ,  "Upload .csv (small file only)")
    
    
    # https://data.ontario.ca/dataset/deaths-involving-covid-19-by-vaccination-status
    # https://data.ontario.ca/dataset/deaths-involving-covid-19-by-vaccination-status/resource/2aa6e2ce-40de-4910-a737-81762e014b0b
    # https://data.ontario.ca/dataset/1375bb00-6454-4d3e-a723-4ae9e849d655/resource/2aa6e2ce-40de-4910-a737-81762e014b0b/download/deaths_by_vac_status.csv
    # URL: https://data.ontario.ca/dataset/1375bb00-6454-4d3e-a723-4ae9e849d655/resource/2aa6e2ce-40de-4910-a737-81762e014b0b/download/deaths_
    
  )
}) 
# )



splitLayout(
  actionButton("button.add_data", "Add data!", class = "btn-success",  width="100%"), 
  actionButton("button.reset", "Reset all", class = "btn-warning",  width="100%")
)



hr()

```

```{r UI: select.columns var.X}

renderUI({   
  req(r$dtAll); 
  sliderInput('slider.sample_size', 'Sample Size', min=1, max=nrow(r$dtAll), value=nrow(r$dtAll))
})

renderUI({   
  req(r$dt);   
  selectInput( "select.columns", "Choose columns:", r$dt %>% names,
               c("Date", "GEO", "val_norm"),
               # r$dt %>% names %>% .[1:5],
               # c("Date", "val_norm", "Characteristics"),
               multiple = T,  width="100%")
})


renderUI({   
  req(r$dt);  
  actionButton("button.apply", "Apply changes!", class = "btn-primary",  width="100%") 
})




renderUI({   
  req(r$dtAll);   
  checkboxGroupInput("check.grid_or_plot", NULL,
                     c("Show Grid" = "grid", "Show Graph" = "graph"), 
                     c("grid", "graph"), inline = T )
})


####### START var.X. Maybe automate it?

# 
# aTypes <- c("Date", "Time", "numeric", "factor")
# renderUI({
#   selectInput("type.var.X", NULL, aTypes, r$dt0[[input$var.X]] %>% class)
# })
# 
# renderUI({
#   r$dt0[[input$var.X]] %>% unique()
# selectInput('choice.var.X', "Select:", r$dt0[[input$var.X]] %>% unique(), multiple=T) #, selectize=F, size=5 )
# })

# renderUI({
#   r$dt0[[input$var.X]] %>% unique()
# selectText('filter.var.X', "Filter:", multiple=T, 1) 
# })

# observe( {
#   
#   req(r$dt0)
#   
#   r$dt0[[input$var.X]] <- switch(input$type.var.X,
#                                        "factor" = r$dt0[[input$var.X]] %>% as.ordered()
#   )
# 
#   r$dt00 <- r$dt0[ input$var.X %in% input$choice.var.X]
# }) 

# checkboxInput("var.X.time", strong( "This is the time/date variable" ) , T)
# 
# renderUI({   req(input$var.X.time);  
#   dt <- r$dt
#   dt[[input$var.X]] <- dt[[input$var.X]] %>% as.Date()
# })

####### END


renderUI({   
  req(r$dt0);
  cols <- r$dt0 %>% names
  # cols2 <- names(r$dt0[sapply(r$dt0, is.factor)])
  cols2 <- dt.findCategoricalColumns (r$dt0)
  
  flowLayout(
    selectInput( "var.X", "X:",  cols),
    selectInput( "var.Y", "Y:",  cols),
    selectInput( "var.Colour", "Colour:",  c("None", cols)),
    selectInput( "var.Size", "Size:",  c("None", cols)),
    selectInput( "var.facetX", "Vertical  facets:",  c(None='.', cols2)),
    selectInput( "var.facetY", "Horizontal facets:",  c(None='.', cols2)),
    
    checkboxInput('jitter', 'Jitter', value = F),
    checkboxInput('smooth', 'Smooth', value = F),
    checkboxInput('line', 'Lines', value = F)
  )
})


```




```{r UI: filter and transform}




# 
# 
# renderUI({   
#   req(r$dt);   
#   actionButton( "button.filters", "Add Filter",width = "100%")
# })
# 
# 
# renderUI({   
#   req(r$dt);   
#   textInput( "text.search", NULL, placeholder="Enter keyword and press Search")
# })
# 




renderUI({   
  req(r$dt);   
  actionButton( "button.rename", "Rename fields and values", width = "100%")
})


renderUI({ req(r$dt);
  popify(
    textInput("filter", "Enter filter:", "", 
              placeholder="(GEO %in% c('AB', 'BC')) & (sex=='male') & (year>2015)", width="100%"),
    title = "Use R syntasis to define flters. ",
    content = paste0( "Example:
  '(GEO %in% c('AB', 'BC')) & (sex=='male') & (year>2015)' ") ,
  placement = "left", trigger = "hover"
  )
  
})




# # Rename variable names and values
# 
# 
# splitLayout(
#   renderUI({
#     req(input$button.rename)
#     if (input$button.rename %% 2 == 0)
#       textInput("textA", "Replace this text ..")
#   }),
#   renderUI({
#     req(input$button.rename)
#     if (input$button.rename %% 2 == 0)
#       textInput("textB", ".. with this text")
#   })
# )
# 
# splitLayout(
#   renderUI({
#     if (input$button.rename %% 2 == 0)
#       textInput("colA", "Rename this variable name ..")
#   }),
#   renderUI({
#     if (input$button.rename %% 2 == 0)
#       textInput("colB", ".. with this variable name")
#   })
# )


# 
# renderUI({   
#   req(r$dt);   
#   actionButton("button.join", "Join with another dataset",  class =  "btn-primary", width="100%")
# })
# 




```


```{r SERVER: observe}
shinybusy::add_busy_bar(color = "Red", height = "40px", centered = T)

# *** r$dtAll=dt=dt0 ***#####


observeEvent(input$button.add_data, {
  req(input$select.data_source) 
  req(input$select.data_address) 
  #   if (str_length(input$select.data_address) > 2) {
  r$dtAll <- switch ( input$select.data_source,
                      "local" = fread(input$select.data_address, stringsAsFactors = F),
                      "url" = fread(input$select.data_address, stringsAsFactors = F),
                      "upload" = {
                        
                        file <- input$select.data_address;
                        ext <- tools::file_ext(file$datapath);
                        req(file);
                        validate(need(ext == "csv", "Please upload a csv file"));
                        fread(file$datapath, stringsAsFactors = T)
                      },
                      "statcan" = cansim::get_cansim(input$select.data_address) %>%  setDT() , # "13-10-0810-01"
                      
                      "ontario" = fread(ckanr::resource_show(id = input$select.data_address) [["url"]])
  )
  
  # r$dtAll <- readr::type_convert(r$dtAll) %>% setDT

    # r$dt <- r$dtAll[sample(nrow(r$dtAll), input$slider.sample_size)] # CRUSHES  
  r$dt <- copy(r$dtAll)
  
  r$columns <- input$select.columns
   
  r$dt0 <- r$dt [, r$columns , with=F]
  r$dt0 <- copy(r$dtAll)
  
  
  req(r$dtAll)
  # if ( ! is.null(r$dtAll) ) {
  #   r$filesOpened <- r$filesOpened + 1
  # }
})


# observe({
observeEvent(input$button.apply, {
  
  # req(r$dtAll, input$slider.sample_size, input$select.columns)
    req(r$dtdt, input$select.columns)
  
  
  # r$dt <- r$dtAll[sample(nrow(r$dtAll), input$slider.sample_size)] # CRUSHES
  r$columns <- input$select.columns
  
      
  r$dt0 <- r$dt [, r$columns , with=F]
  
  # tryCatch({
  #   
  #   if (is.null(r$filter)) {
  #     r$dt0 <- r$dt [, input$select.columns, with=F]
  #   } else {
  #     r$dt0 <- r$dt [eval(parse(text = r$filter)), input$select.columns, with=F]
  #   }
  # }, 
  # error = function(err) {
  #   showNotification(err, duration = 10)
  #   return(err)
  # }
  # 
  # )
  
  
}) 



observe( {
  r$variables <- c(input$var.X,  input$var.Y, input$var.Colour, input$var.Size, input$var.facetX, input$var.facetY) 
}) 



observeEvent(input$button.apply, {
  
  r$filter=input$filter
  
  # if  (str_length(input$textA)>0 & str_length(input$textB)>0) {
  #   cols <- names(r$dt0)
  #   r$dt[, (cols) := lapply(
  #     .SD, function (x) { gsub(input$textA, input$textB, x) } ),
  #     .SDcols = cols]
  # }
  # 
  # if  (str_length(input$colA)>0 & str_length(input$colB)>0) { 
  #   setnames(r$dt, input$colA, input$colB)
  # }
  
})




```


<!-- # Data Preview -->

# Visualize
<!-- # Extract -->


## ******* Tables ******* 

<!-- ## ********************** {.tabset} -->


<!-- Grid   -->

```{r OUT: Grid}
renderUI({
  req(r$dt);
  fluidPage(
    fluidRow(
      column(width=6, 
             renderUI({
               req(r$dt);
               # checkboxInput("a0.search.details", strong( "Show selected columns only" ), T )
               
               checkboxGroupInput("check.show", NULL,
                                  c("Show all columns" = "selected.columns",
                                    "Show interactive" = "interactive") )
             })
      ),
      column(width=6, 
             renderUI({
               req(r$dt);
               numericInput( "rows", "Number of top/bottom rows to show", width="100%", 2, 1, r$dt %>% nrow(),1 )
             })
      )
    ),
    fluidRow( 
      column (width=12, 
              renderUI({
                req(r$dt, input$button.add_data);
                if (input$button.add_data > 0)
                  
                  radioButtons ("check.printDT", "Show:",  width="100%", inline = T,
                                choices = c(
                                  "Summary" = "summary",
                                  "Summary (Categorical)" = "summary2",
                                  "Structure" = "str",
                                  "Table "= "table",
                                  "Table (with types)" = "head",
                                  "Interactive Table (Search/Save)" = "interactive"
                                  
                                ), selected = "head"
                  )
              })
      )
    ),
    
    fluidRow( 
      column (width=12, 
              
              
              # print result #####
              
              renderUI({
                
                # dt <- r$dt
                req(r$dt)
                req(input$check.printDT)
                
                if ( "selected.columns" %in% input$check.show ) { # a0.search.details == T
                  dt <- r$dt
                } else {
                  dt <- r$dt0
                }
                # dt %>% renderPrint
                
                switch (input$check.printDT,
                        "nothing" = NULL,
                        "str" = renderPrint( dt %>% str),
                        "summary" = renderPrint( dt %>% summary),
                        "summary2" = {
                          
                          cols = dt %>% names
                          dt0 <- copy(dt)
                          dt0[, (cols):=lapply(.SD, as.character), .SDcols = cols]
                          dt0[, (cols):=lapply(.SD, as.ordered), .SDcols = cols]
                          
                          renderPrint( dt0 %>% summary)
                        },
                        "head" = renderPrint( dt[c(1:input$rows, (.N-input$rows+1):.N) ] ),
                        
                        "table" =   renderTable( 
                          dt[c(1:input$rows, (.N-input$rows+1):.N) ], 
                          rownames = T ),
                        
                        # dt0 <- r.dtExcess() [, Date:=format(Date,'%Y-%m-%d')] [order(-Date)]
                        
                        "interactive" = renderDataTable( datatable.title( dt, "Click on column names to sort. Filter by typing in boxes under column names. Save selected data by clicking the buttons") )
                        
                )
                
                
                
              })
              
      ) # column
    ) # fluidrow
  ) #fluidpage
  
}) # renderUI
```





```{r ggplot, out.width = "100%", out.height = "100%"}

# https://garrettgman.github.io/rmarkdown/flexdashboard/shiny.html#component_layout
# https://shiny.rstudio.com/reference/shiny/latest/fillRow.html
# https://shiny.rstudio.com/articles/gadget-ui.html#fillrowfillcol
# https://jjallaire.shinyapps.io/shiny-ggplot2-brushing/
# https://jjallaire.shinyapps.io/shiny-ggplot2-diamonds/

# ```{r ggplot, out.width = "10", out.height = "10"} {data-width=400}

renderUI({
  req(r$dt);
  checkboxInput("plot.interactive", "Show interactive" , F )
})

# theme_set(theme_bw())

renderUI({ 
  
  req(r$dt0);
  dt <- r$dt0
  
  
  # g <- NULL
  
  if (T) {
    
    # if (input$var.Y != "") {
    
    g <- 
      ggplot(dt, aes_string(x=input$var.X, y=input$var.Y)) +
      # ggplot2::diamonds %>%  ggplot(aes_string(x="table", y="price")) +
      
      geom_point() + 
      # coord_flip() +
      #       scale_y_continuous(breaks = (0:10)*10,limits=c(0,100)) +
      # scale_fill_brewer(palette = "Greens", direction = 1) +   #scale_fill_grey(0.3, 0.9) +
      
      
      
      # coord_cartesian(ylim = c(0, 100)) +
      # ylim(0, 100) + # coord_cartesian(xlim = c(0, 100))
      # guides(fill="none", col="none") +
      theme_bw() +
      theme(legend.position = "bottom") +
      
      #  # scale_y_log10(breaks = c(1, seq(0, 1, 0.1))) +
      #     scale_y_log10(breaks = trans_breaks('log10', function(x) 10^x) ) +
      # # scale_y_log10(breaks = trans_breaks('log10', function(x) 10^x), labels = trans_format('log10', math_format(10^.x))) +
      
      labs(
        # title= title,
        # subtitle=paste0("Dates: ", from, " - ", to),
        # # caption = "Change since previous period is marked by arrow.",
        # caption="Green: Current period. Red: Previous period",
        # # caption="Cross indicates historical average. Change since last period marked by arrow",
        # #  y="Transactions",
        y=NULL,
        x=NULL
      ) 
    
    
    
    if (input$var.Colour != 'None')
      g <- g + aes_string(color=input$var.Colour)
    if (input$var.Size != 'None')
      g <- g + aes_string(size=input$var.Size)
    
    facets <- paste(input$var.facetX, '~', input$var.facetY)
    if (facets != '. ~ .')
      g <- g + facet_grid(facets, scales = "free")
    
    if (input$jitter)
      g <- g + geom_jitter()
    if (input$smooth)
      g <- g + geom_smooth()
    if (input$line)
      g <- g + geom_line()
    
    
    # renderPlot(g)
    
    if (input$plot.interactive) {
      renderPlotly( g %>% ggplotly )
    } else {
      renderPlot(g)
    }
    # 
  }
})



```


<!-- # Transform -->
<!-- # Compute Statistics -->

```{r Tabulate, eval=FALSE, include=FALSE}


```

<!-- # Modify data {-} -->

```{r echo=FALSE}

# dt[c(1:10, (.N-9):.N)] %>% datatable(filter="top") %>% htmlwidgets::saveWidget(paste0(path,".html"))
```


<!-- # Data Catalog -->
# Search


<!-- ### Search results -->

You can search dataset by browsing official data catalogs at the links provided, or by entering a keyword below.

Official data catalogs:  

- https://www150.statcan.gc.ca/n1/en/type/data
- https://data.ontario.ca/

```{r ---search}

flowLayout(
  # renderUI({
  #   if (input$a1.search.yes.no == "Yes") {
  #     selectInput("a0.search.what",  "Select source:",
  #                 c("StatCan Tables", "Open Ontario data") )
  #   }
  # }), 
  renderUI({
    # if (str_length( input$select.data_address) < 3 ) 
    {
      # if (input$a1.search.yes.no == "Yes") {
      textInput("text.keyword", "Enter keyword", "vital")
    }
  }), 
  
  renderUI({   
    req(input$text.keyword);  
    actionButton("button.search", "Search!", class = "btn-primary") 
  })
  
)


r.dt0  <- eventReactive(input$button.search, {
  req(input$text.keyword)
  if (input$select.data_source == "statcan") {
    dt0 <- search_cansim_cubes(input$text.keyword) %>% setDT()
    
    # "frequencyCode", , "subjectEn"
    cols <- c("cansim_table_number", "cubeTitleEn", "dimensionNameEn", "surveyEn")
    dt0 <- dt0[,cols, with =F]
    dt0
    
  } else { # "ontario") {
    
    ckanr_setup(url = "https://data.ontario.ca/")
    res <- resource_search(q = paste0("name:",input$text.keyword), as = "table")
    # res$count #7
    dt0 <- res$results %>% setDT
    cols1 <- c("id", "name", "original_url", "description", "data_range_start", "data_range_end")
    dt0 <- dt0[,cols1, with =F]
  }
  dt0
})

observe({
  r$dt.found <- r.dt0()
})

# Show result (downloaded table) --- --

flowLayout(
  renderUI({
    req(r.dt0())
    h4( paste0("Found ", r.dt0() %>% nrow," tables." ) )  # Paste the table id/No into box."
  }),
  renderUI({
    if (r.dt0() %>% nrow > 0) {
      # selectInput("a0.search.details",  "Show details:",  c("Yes", "No"), "No")
      checkboxInput("a0.search.details", strong( "Show full description" ) )
    }
  }),
  renderUI({
    if (r.dt0() %>% nrow > 0)  {
      checkboxInput("a0.search.interactive",  strong("Show interactive" ) )
      # selectInput("a0.search.interactive",  "Show interactive:",   c("Yes", "No"), "No" )
    }
  })
)

renderUI({
  # if (input$a1.search.yes.no == "Yes"  & r.dt0() %>% nrow > 0) {
  req(r.dt0())
  dt <- r.dt0()
  if (input$a0.search.details == F) {
    dt <- dt[,1:2]
  }
  
  if (input$a0.search.interactive==T) {
    renderDataTable( datatable.title( dt, "Click on column names to sort. Filter by typing in boxes under column names. Press Buttons above to save selected data.") ) # paste0("Keyword: ", input$text.keyword)
  } else {
    renderTable( dt )
  }
  # }
  
})


```


```{r popups+resets}

observeEvent( input$button.reset, { # you may wish to choose which settings to keep
  reset.reactive()
})

d7.reset_input <- function() {
  # reset ALL inout when input$reset_input is changed
  
  # if (T) {
  # https://stackoverflow.com/questions/24265980/reset-inputs-button-in-shiny-app
  
  initialInputs <- isolate(reactiveValuesToList(input))
  
  observe({
    # OPTIONAL - save initial values of dynamic inputs
    inputValues <- reactiveValuesToList(input)
    initialInputs <<- utils::modifyList(inputValues, initialInputs)
  })
  
  observeEvent(input$button.reset, {
    for (id in names(initialInputs)) {
      value <- initialInputs[[id]]
      # For empty checkboxGroupInputs
      if (is.null(value)) value <- ""
      session$sendInputMessage(id, list(value = value))
    }
  }
  )
}

d7.reset_input()



# Pop-up window
# https://stackoverflow.com/questions/48523338/how-can-i-add-a-message-box-in-r-shiny
observeEvent(input$button.reset, {
  showModal(modalDialog(
    title = "* Warning *",
    paste("The following inputs have been reset:", paste(unlist(reactiveValuesToList(input)), collapse = ", ")),
    easyClose = TRUE,
    footer = "Press anywhere to continue" # NULL
  ))
})

# observeEvent(input$button.search, {
#   showModal(modalDialog(
#     title = "Search launched",
#     "Note it can take up to a minute to complete the search",
#     easyClose = TRUE,
#     footer = "Press anywhere to continue" # NULL
#   ))
# })

observeEvent(input$button.go, {
  showModal(modalDialog(
    title = "File being loaded",
    "Note it can take some time for large files",
    easyClose = TRUE,
    footer = "Press anywhere to continue" # NULL
  ))
})



```


<!-- ```{r 09_data_info.Rmd, child = '09_data_info.Rmd'} -->
<!-- ``` -->


# Debug {data-orientation=columns}


##

<!-- ### Debug window -->

```{r Debug1, echo=F}
actionButton("button.debug", "Click here to show/hide debug information", width="100%")
# observeEvent(input$button.debug,
#                 renderPrint(reactiveValuesToList(input) )
# )

renderUI ({
  if (input$button.debug %% 2 == 0)
    renderPrint(reactiveValuesToList(r))
})

# r$dt[1:2] %>% renderPrint
# r$dt0[1:2] %>% renderPrint




# renderUI ({
#   
#   dt <- r$dt
#   req(dt)
#   
#   if ( "selected.columns" %in% input$check.show ) { # a0.search.details == T
#     # dt <- dt[,1:2]
#     dt <- r$dt0
#   }
#   dt %>% renderPrint
# })


```


##

```{r Debug2, echo=F}

renderText(paste0("Working directory: ", getwd()))

# 
# actionButton("button.debug", "Click here to show/hide debug information", width="100%")


# observeEvent(input$button.debug,
#                 renderPrint(reactiveValuesToList(input) )
# )


renderUI (
  if (input$button.debug %% 2 == 0)  
    verticalLayout(
      renderPrint(reactiveValuesToList(input) )
      
    )
)

```
