---
title: "Interactive Open Canada Data Catalog"
subtitle: "URL: <https://o-canada.shinyapps.io/data> (Source: <https://github.com/open-canada>)"
output: html_document
runtime: shiny
resource_files:
- 09_data_info.Rmd
- explorer.Rmd
- list.Rmd
---

```{r global, echo=F, include=FALSE}
knitr::opts_chunk$set(echo = F)

if (T) {  
  library(shiny)
  library(shinyBS) # https://stackoverflow.com/questions/33925430/shiny-plot-results-in-popup-window https://stackoverflow.com/questions/61667924/create-a-small-window-to-describe-the-meaning-of-filters-in-shiny
  
  library(magrittr);   library(ggplot2); 
  library(dtplyr)
  
  library(lubridate,  quietly=T); options(lubridate.week.start =  1)
  library(data.table); options(datatable.print.class=TRUE); options(datatable.print.rownames = T)
  # options(datatable.print.nrows = 300) # 100
  options(datatable.print.topn=3) # 5
  
  # library(dygraphs);   
  # library(ggpubr)
  library(DT); 
  library(plotly);   
  library(GGally)
  library(stringr); library(forcats) 
  library(ckanr);   library(cansim)
  
  options(digits = 3)
  # options(max.print = 100) # 1000
  options(scipen = 999) # remove scientific notation
  
  
  if ( shiny::isRunning() ) {  
    r <- reactiveValues()
  } else {
    r <- list()
  }
  
  reset.reactive <- function() {
    r$dt.found <- r$dtAll <- r$dt <-   r$dt0 <-   NULL
    r
  }
  
  r <- reset.reactive() 
}



datatable.title <- function(dt, title=NULL) {
  # https://rstudio.github.io/DT/options.html
  dt %>% DT::datatable (
    filter = "top",  caption = title, rownames=T, extensions =  c('ColReorder', 'Buttons'),
    options = list(
      dom = 'Blfrtip',
      # paging = FALSE, 
      # pageLength=50, scrollX='400px', # horizontal scroll
      scrollX = TRUE,       scrollY = "600px",
      
      colReorder = TRUE,
      # lengthMenu = list(c(10,25,100,-1), c(5,10,25,50,"All")),
      lengthMenu = list(c(10,25,100,-1), c(5,10,50,"All")),
      buttons = c('copy', 'csv', 'excel', 'pdf', 'print') 
    ) )
}


```



#### Data Sources:


- https://www150.statcan.gc.ca/n1/en/type/data
- https://data.ontario.ca/


<!-- "Interactive Open Canada Data Catalog" Web App is developed to facilitate finding, exploring and exporting Open Canada datasets. -->
<!-- You can use this Web App to search, preview and export Open Canada datasets. -->

<!-- Open Canada data catalogs accessed by this App: -->


#### Related products: 

- [Open Canada Vital Statistics (Deaths) tracker](https://o-canada.shinyapps.io/vitals/)
<!-- The search results will be shown below. -->

<!-- Source code of this App is available on  [GitHub](https://github.com/open-canada/vitals/tree/main/R). -->



If you know the Table number, enter it below and then click 'Load data!" button.
If you don't know the Table number, enter the search keyword and click 'Search!" button.
A list of some Open Canada data tables is also  available [here](https://o-canada.shinyapps.io/data/list.Rmd).


Note: It can take some time to search the data catalog. The progress bard will blink while data is being loaded and processed.   
The results will be shown below. You can filter, sort and export them (e.g., as .csv or .xls) using the options that will be provided below, once the dataset is loaded.

<!-- # Make selection {.sidebar} -->



```{r ____Select Data source and address, echo=FALSE}





hr()

h3("Preview and export the Dataset by Table number:")

splitLayout(
  
  
  popify(
  # tipify(
    selectInput(
      "select.data_source",  
      "Select data source:",  width="100%",
      choices = c( 
        
        "Statistics Canada" = "statcan",
        "Ontario open data (data.ontario.ca)" = "ontario",
        "URL"= "url"
        # "Local hard drive" = "local"
        # "Upload "= "upload"
      ),
          selectize = F
    # size = 5, # only for selectize=F
    ),
    "Tip:",
    "It can take for up to one minute to load data",
      placement = "top", trigger = "hover"
  ),
  
  
  renderUI({ 

    switch ( input$select.data_source,
             "url" =  textInput ("select.data_address", "Type URL: ",  
                                 "https://health-infobase.canada.ca/src/data/covidLive/vaccination-coverage-map.csv",
                                 
            placeholder="Enter valid URL address of the dataset", width="100%" ),
            
             "statcan" =  textInput("select.data_address",  "Enter StatCan Table number:",   "13-10-0768-01", width="100%"),
            
             "ontario" =   textInput("select.data_address",  "Enter Ontario Table number: ",  "97622ce6-c06a-4970-afe5-be540c748f24", width="100%") 
    )
    
  })
  
)

p()
actionButton("button.add_data", "Load data!", class = "btn-success",  width="100%")





```



```{r ____open file, echo=FALSE}



observeEvent(input$button.add_data, {
  req(input$select.data_address) 
  
  r$select.data_address <- input$select.data_address
  
  r$dtAll <- NULL
  r$dt <- NULL
  r$select.columns <- NULL
  
  if (input$select.data_source == "statcan") {
    r$select.data_address <- "13-10-0768-01" 
    r$dtAll = cansim::get_cansim(r$select.data_address) %>%  setDT()
    
  } else   if (input$select.data_source == "ontario" ) {
    # r$select.data_address <- "97622ce6-c06a-4970-afe5-be540c748f24" 
    r$dtAll = fread(ckanr::resource_show(id = r$select.data_address) [["url"]])
  }     else if (input$select.data_source ==  "url") {
    r$dtAll = fread(input$select.data_address, stringsAsFactors = T)
  }
  
  
  
  # cols  <- r$dtAll [, which(sapply(.SD, is.character))] 
  # r$dtAll[, (cols):=lapply(.SD, as.ordered), .SDcols=cols]
})

p()

# >>> choose columns -----------------------------
renderUI({
  req(r$dtAll);
  selectInput( 
    "select.columns", "Select columns (Use DELETE button to remove):", 
    r$dtAll %>% names,
    r$dtAll %>% names %>% .[1:3],
    # r$dtAll %>% names, 
    selectize = T,
    # size = 5, # only for selectize=F
    
    # c("Date", "val_norm", "Characteristics"),
    multiple = T,  width="100%")
  
  
})


observe( {
  
  req(r$dtAll)
  # req(r$dtAll,r$select.columns)
  
  r$select.columns <-  input$select.columns
  # r$slider.sample_size <- input$slider.sample_size
  
  # r$dt <- r$dtAll
  
  r$dt <- r$dtAll[, r$select.columns, with=F]
  # r$dt <- r$dtAll %>% select(all_of(input$select.columns)) %>% as.data.table()
  
  
  # r$dt0 <- r$dt[ sample( nrow(r$dt), input$slider.sample_size) ]
  
  
  # colsDate <- r$dt[1] %>% ymd() %>% is.Date() %>% which; colsDate
  # r$dt [, (colsDate):=lapply(.SD, ymd), .SDcols=colsDate ]
  # 
  # colsChar  <- r$dt[, which(sapply(.SD, is.character))]; colsChar
  # r$dt [, (colsChar):=lapply(.SD, as.ordered), .SDcols=colsChar ]
  
}) 


renderUI({
  req(r$dtAll);
  
  radioButtons ("check.printDT", "Show:",  width="100%", inline = T,
                choices = c(
                  "Nothing" = "nothing",
                  "Graph" = "pairs",
                  "Structure" = "str",
                  "Summary" = "summary",
                  "Summary (Categorical)" = "summary2",
                  "Table "= "table",
                  # "Table (with types)" = "head",
                  "Interactive Table (Search/Save)" = "interactive"
                ), selected = "interactive"
  )
})



renderUI({
  req(r$dtAll);
  splitLayout(
    
    # sliderInput('slider.sample_size', 'Sample Size', min= as.integer(nrow(r$dtAll)/100 +0.5 ) , max=nrow(r$dtAll), value=nrow(r$dtAll)),
    

    checkboxGroupInput("check.show", NULL,
                       c("Display all columns" = "selected.columns")
                       ),
                         # "Use interactive mode" = "interactive") ), 
    
    numericInput( "rows", "Number of top/bottom rows to show", width="100%", 2, 1, r$dt %>% nrow(),1 )
  )
})




# 
# ```
# 
# ```{r Grid, eval=T, include=T, , out.width = "6", out.height = "7"}

hr()

renderUI({
  
  # req(r$dt,button.show_data_preview)
  req(r$dt)
  
  if (T) { #input$button.show_data_preview %% 2 == 0) {
    
    if ( "selected.columns" %in% input$check.show ) { 
      dt <- r$dtAll
    } else {
      dt <- r$dt
    }
    
    
    
    switch (input$check.printDT,
            "nothing" = NULL,
            "str" = renderPrint( dt %>% str),
            "pairs" =  r$dt %>% plot %>% renderPlot,
            
            "summary" = renderPrint( dt %>% summary),
            "summary2" = {
              
              cols = dt %>% names
              dt0 <- copy(dt)
              dt0[, (cols):=lapply(.SD, as.character), .SDcols = cols]
              dt0[, (cols):=lapply(.SD, as.ordered), .SDcols = cols]
              
              renderPrint( dt0 %>% summary)
            },
            "head" = renderPrint( dt[c(1:input$rows, (.N-input$rows+1):.N) ] ),
            
            "table" =   renderTable( 
              dt[c(1:input$rows, (.N-input$rows+1):.N) ], 
              rownames = T ),
            
            # dt0 <- dt0[, Date:=format(Date,'%Y-%m-%d')] [order(-Date)]
            
            "interactive" = {
              
              renderDataTable( datatable.title( dt, "Click on column names to sort. Filter by typing in boxes under column names. Save selected data by clicking the buttons") )
            }
            
    )
    
  }
  
})


  
  # r$dt %>% ggpairs %>% renderPlot
  
  # r$dt %>% plot %>% renderPlot
  
  # r$dt %>% ggpairs (columns = 2:5, mapping = aes(color = "GEO", shape="Sex"))
  # r$dt %>% ggpairs (mapping = aes(color = "GEO"))
  


```




```{r dt.found, echo=FALSE}

h3("Find dataset by keyword:")

splitLayout(
  textInput("text.keyword", NULL, value="deaths",
            placeholder="Enter a search term (e.g., 'deaths') and click Search!", width="100%"),
  actionButton("button.search", "Search!", class = "btn-primary",  width="100%") 
)


p()



# ```
# 
# ```{r dt.found}


shinybusy::add_busy_bar(color = "DodgerBlue", height = "40px", centered = T)



observeEvent(input$button.search, {
  req(input$text.keyword)
  if (input$select.data_source == "statcan") {
    r$dt.found0 <- search_cansim_cubes(input$text.keyword) %>% setDT()
    
    # "frequencyCode", , "subjectEn"
    cols <- c("cansim_table_number", "cubeTitleEn", "dimensionNameEn", "surveyEn")
    r$dt.found <- r$dt.found0[,cols, with =F]
    
    
  } else { # "ontario") {
    r$text.keyword <- input$text.keyword  
    
    ckanr_setup(url = "https://data.ontario.ca/")
    res <- resource_search(q = paste0("name:",r$text.keyword), as = "table")
    
    
    # res$count #7
    
    if(res$count>0) {
      r$dt.found0 <- res$results %>% setDT
      
      cols1 <- c("id", "name", "original_url", "description", "data_range_start", "data_range_end", "last_modified")
      r$dt.found <- r$dt.found0[,cols1, with =F]
    }
    else {
      r$dt.found0 <-  r$dt.found <- data.table()
      
    } 
  }
})


# Show result (downloaded table) --- --



renderUI ({
  req(r$dt.found)
  actionButton("button.show_search_results", "Click here to show/hide search results", width="100%")
})

renderUI ({
  req(r$dt.found0)
  # req(input$button.show_search_result)
  r$bSearchOn = T
  # if (input$button.show_search_results %% 2 == 0) {
  if(T)  {
    
    flowLayout(
      
      h4( paste0("Found ", r$dt.found0 %>% nrow," tables." )) ,  # Paste the table id/No into box.",
      
      checkboxInput("a0.search.details", strong( "Show full description" ) ),
      checkboxInput("a0.search.interactive",  strong("Show interactive" ) )
      
      
    )
  }
})


renderUI({
  req(r$dt.found)
  # req(r$dt.found,input$a0.search.interactive,input$a0.search.details)
  if (input$button.show_search_results %% 2 == 0) {
    
    if (input$a0.search.details == F) {
      dt <- r$dt.found # dt[,1:2]
    } else {
      dt <- r$dt.found0
    }
    
    if (input$a0.search.interactive==T) {
      renderDataTable( datatable.title( dt, "Click on column names to sort. Filter by typing in boxes under column names. Press Buttons above to save selected data.") ) # paste0("Keyword: ", input$text.keyword)
    } else {
      renderTable( dt )
    }
    
  }
  
})


```


```{r popups+resets, eval=FALSE, include=FALSE}

p()
actionButton("button.reset", "Reset all", class = "btn-warning",  width="100%")

d7.reset_input <- function() {
  # reset ALL input when input$reset_input is changed
  
  # https://stackoverflow.com/questions/24265980/reset-inputs-button-in-shiny-app
  
  initialInputs <- isolate(reactiveValuesToList(input))
  
  observe({
    # OPTIONAL - save initial values of dynamic inputs
    inputValues <- reactiveValuesToList(input)
    initialInputs <<- utils::modifyList(inputValues, initialInputs)
  })
  
  observeEvent(input$button.reset, {
    for (id in names(initialInputs)) {
      value <- initialInputs[[id]]
      # For empty checkboxGroupInputs
      if (is.null(value)) value <- ""
      session$sendInputMessage(id, list(value = value))
    }
  }
  )
}

observeEvent( input$button.reset, { # you may wish to choose which settings to keep
  r <- reset.reactive()
  d7.reset_input()
})





# Pop-up window
# https://stackoverflow.com/questions/48523338/how-can-i-add-a-message-box-in-r-shiny
observeEvent(input$button.reset, {
  showModal(modalDialog(
    title = "* Warning *",
    "All settings and inputs have been reset",
    # paste("The following inputs have been reset:", paste(unlist(reactiveValuesToList(input)), collapse = ", ")),
    easyClose = TRUE,
    footer = "Press anywhere to continue." # NULL
  ))
})



```




```{r STOP_HERE, eval=F, include=FALSE}
knitr::knit_exit()
```


<!-- ## Technical information -->

<!-- ### Debug window -->

```{r Debug1, echo=F, include=T}
hr()
actionButton("button.debug", "Click here to show/hide debug information", width="100%",   class="btn-secondary")
# observeEvent(input$button.debug,
#                 renderPrint(reactiveValuesToList(input) )
# )

renderUI (
  if (input$button.debug %% 2 == 1) {
    splitLayout(
      
      
      renderPrint(reactiveValuesToList(input) ),
      
      renderPrint(reactiveValuesToList(r))
      
    )
  }
)

```