---
title: "OpenCanada.info: Ontario"
output: flexdashboard::flex_dashboard
runtime: shiny
---


```{r  include=FALSE}
library(ckanr);  
ckanr_setup(url = "https://data.ontario.ca/")

knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE)
# source("opendata-base.R")
source("lib_opendata.R")
```


```{r odON_sources.Rmd, child = 'odON_sources.Rmd'}
```



<!-- # Deaths {data-orientation=rows, data-navmenu="Ontario"} -->


```{r Vital Events Data by Month}


ckan = "58e648f1-ae1e-4ed7-9003-7da5983b0a77"	
title = "Cumulative deaths (new methodology)"

```

# Vital Events by Month {data-orientation=rows, data-navmenu="Ontario"}


```{r Vital Events Data by Month}


ckan = "58e648f1-ae1e-4ed7-9003-7da5983b0a77"	
title = "Cumulative deaths (new methodology)"


self <- COpenData$new(
  myname="odOntario.death.registrations",
  info=c(
    title = "Death registrations in Ontario",
    webpage = NA,
    comment=NA
  ),
  data = c (
    origin="ckan",
    ckan = "2925c1ea-8313-4e9b-bdea-344e521d2298"
  )
)
  
self <- COpenData$new(
  myname="odOntario.vitals.by.month",
  info=c(
    title = "Vital Events Data by Month",
    webpage = "https://data.ontario.ca/en/dataset/vital-events-data-by-month",
    comment="Includes births and stillbirths"
  ),
  data = c (
    origin="ckan",
    ckan = "97622ce6-c06a-4970-afe5-be540c748f24",
    csv = "https://data.ontario.ca/dataset/e100b1d5-b7fb-40fd-b7a0-50289d13c574/resource/97622ce6-c06a-4970-afe5-be540c748f24/download/vital_events_data_by_month_1994-2022_q2.csv"
  )
)

self$restore.me()

# self %>% od.fread(origin=self$data[["origin"]])
self %>% od.fread(origin="ckan")
# self %>% od.fread(origin="csv.local")

self %>% od.view()

self$fLte.Define(
  function (self) {
    dt <- self$dt
    dt %>% names
    col <- "Month/Mois"
    dt[, (col):=fct_inorder(get(col))] 
    dt[, (col) := as.integer(get(col))]
    dt[, Date:=ym(paste(`Year/Année`, get(col)) ) ]
    
    dt[, ( "Marriages/Mariages" ):= NULL]
    dt[, c( "Month/Mois", "Year/Année" ):= NULL]   
    setnames(dt, "Stillbirths/Mortinaissances", "Stillbirths") 
    setnames(dt, "Live Births/Naissances vivantes", "Live Births") 
    setnames(dt, "Deaths/Dècés", "Deaths")
    
    
    dt [ , `Stillbirths per thousand Total Births` := round (1000 *`Stillbirths` / (Stillbirths+`Live Births`),0)][]  
    dt [ , `Live Births vs. Deaths` := round (`Live Births` / Deaths,2)][] 

    dt$dummy <- "This dataset does not contain any factors"
    # dt$dummy <- ""
    
    self$dt <- dt
    
    self %>% od.setColumns(
      date="Date",
      factors="dummy",  
      metrics = c( "Live Births", "Deaths","Stillbirths", "Stillbirths per thousand Total Births", "Live Births vs. Deaths")
    )
    
    self$dt %>% setorder(-Date)
    
    self$input$metric <- self$col.metrics[4]
    self$input$date.start[1] <- ymd("2015-01-01")
    self$input$date.start[2] <- self$dateMax
  }
)  
self$fLte(self)
self$col.factors.values
self %>% od.view()
self$store.me()
rm(self)

self$dt

self %>% od.add.value.by.convolution (
  self$input$metric, 3)

self %>% od.plot

# self %>% od.add.value.by.granularity (metric="Weekly", granularity=aMetrics[8])
# self <- self %>% od.add.prepandemic ()


```
  


## --- SIDEBAR ---- {.sidebar data-width="250"} 


## *** {.tabset .tabset-fade} 



### Vital Events Data by Month


### Grid

### Timeseries

### Interactive plot

### Plot 



```





```{r eval=T}
knitr::knit_exit()
```

# Ontario  (TBD) {data-orientation=rows, data-navmenu="Provincial"}

## *** {.tabset .tabset-fade} 


### COVID-19 cases in hospital and ICU

- https://data.ontario.ca/en/dataset?q=vital+statistics
- https://data.ontario.ca/en/dataset?q=covid
- https://data.ontario.ca/datastore/dump/e760480e-1f95-4634-a923-98161cfb02fa?bom=True




```{r}
cOn.CasesICU <- COpenDataOntario$new(
  source = "Ontario",
  title = "COVID-19 cases in hospital and ICU, by Ontario Health (OH) region",
  table = "e760480e-1f95-4634-a923-98161cfb02fa"
)

cOn.CasesICU$ckanr()
cOn.CasesICU$..v()

```


```{r}
cOn.CasesICU2 <- COpenData$new(
  url = "https://data.ontario.ca/en/dataset/availability-of-adult-icu-beds-and-occupancy-for-covid-related-critical-illness-crci",
  csv = "https://data.ontario.ca/dataset/1b5ff63f-48a1-4db6-965f-ab6acbab9f29/resource/c7f2590f-362a-498f-a06c-da127ec41a33/download/icu_beds.csv"
)
```

### Deaths

Source: https://data2.ontario.ca/en/dataset/deaths-by-cause-sex-and-age 
Last Validated Date	2016-10-05
Update frequency	Yearly

### Deaths (new methodology)

Source: 



58e648f1-ae1e-4ed7-9003-7da5983b0a77	Cumulative deaths (new methodology)

```{r}
cOn.Deaths <- COpenData$new(
  title = "Cumulative deaths (new methodology)",
  table = "58e648f1-ae1e-4ed7-9003-7da5983b0a77"
)

cOn.Deaths$dt <- fread( ckanr::resource_show(id = cOn.Deaths$table) [["url"]] )
cOn.Deaths$dt

self <- cOn.Deaths

self$dt


 
  
  r$dtAll <- ckanr::resource_show(id = "2925c1ea-8313-4e9b-bdea-344e521d2298") %>% .["url"] %>% unlist %>% fread #Death registrations in Ontario
  

```


### Deaths by vaccination status


```{r}
cOn.CovidDeathsByDose = COpenData$new(
  source = "Ontario",
  title = "Deaths Involving COVID-19 by Vaccination Status",
  comment = "As of January 26, 2023, data from the date of January 1, 2023 onwards reflect updated population estimates. This update specifically impacts data for the 'not fully vaccinated' category.",
  url = "https://data.ontario.ca/en/dataset/deaths-involving-covid-19-by-vaccination-status",
  csv = 
    "https://data.ontario.ca/dataset/1375bb00-6454-4d3e-a723-4ae9e849d655/resource/2aa6e2ce-40de-4910-a737-81762e014b0b/download/deaths_by_vac_status.csv",
  csv.local = "ON-deaths_by_vac_status.csv",
  frequency = "Daily",
  updated ="Weekly"
  
)
self <- cOn.CovidDeathsByDose
self$dt = fread(self$csv)
# cOnDeathsDose$fread(cached=F)
self$dt.view()
fwrite(self$dt, self$csv.local)

cols  <- self$dt %>% names () %>% .[3:5]; cols
self$dt <- self$dt %>% melt( measure = cols, variable.name = "Doses", value.name = "Deaths", variable.factor = T )

self$dt[, Doses:=str_replace(Doses, "_vac_rate_7ma", "")]

# self$dt %>% setnames(c("date", "age_group"), c("Date", "Age"))

# self$factors <- c()
cOn.CovidDeathsByDose$dt


# cOn.DeathsDose <- self


```



```{r}

h3("Historic deaths by location")

"https://data.ontario.ca/en/dataset/death-registrations-in-ontario-by-location"
"https://data.ontario.ca/dataset/f2d9985b-7195-4a12-8f6c-4efc9adca8d1/resource/2925c1ea-8313-4e9b-bdea-344e521d2298/download/death_registrations_in_ontario_by_location_1940-2022_q2.csv"

"https://data.ontario.ca/en/dataset/death-registrations-in-ontario-by-residence"
"https://data.ontario.ca/dataset/04bb62a9-bd7a-4f2d-bb42-a27c620b1f68/resource/f46643ca-eaaf-40a6-a545-11bc4cc45279/download/death_registrations_in_ontario_by_residence_1980-2022_q2.csv"

"https://data.ontario.ca/en/dataset/comparative-birth-death-marriage-data"
"https://data.ontario.ca/dataset/7d6d02f8-140f-467d-a7c1-861480cadb6d/resource/8f40d667-b379-41c6-b929-cdcce6e0ada7/download/comparative_birth_death_and_marriage_1925-2022_q2.csv"

```