---
title: "OpenCanada.info: PHAC"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r  include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE)
source("opencanada-base.R")
```

# COVID-19 Deaths -- by gender and province {data-orientation=columns, data-navmenu="PHAC"}

## Settings: {.sidebar}

<!-- ## *** {.tabset .tabset-fade}  -->


```{r read PHAC epi, include=F}

################################################################ # 
# https://health-infobase.canada.ca/covid-19/current-situation.html -----
################################################################ # 


# # Figure 2. Weekly number of COVID-19  cases (n=4,297,215) in Canada as of January
# url <- "https://health-infobase.canada.ca/src/data/covidLive/covid19-epiSummary-weeklyEpiCurve.csv"
# #          date cases deaths
# #        <IDat> <int>  <int>
# # 1: 2020-01-18     7      0
# # 2: 2023-01-21  8426     26
# NOT INTERESTING

odCovid.by.province <- COpenData$new(
  myname = "odCovid.by.province",
  info =  c (
    source = "PHAC",
    title = "Deaths by province, relative to province population size, all ages combined",
    comment ="Figure 1. Types of statistics Count (Rate per 100,000 population) of Types of measures total deaths  of COVID-19, Types of statistics province/territory  as of ...",
    url  = "https://health-infobase.canada.ca/covid-19"),
  csv = c(
    live = "https://health-infobase.canada.ca/src/data/covidLive/covid19-download.csv",    local = "covid19-download.csv"
  )
)

# Figure 3. Weekly number of COVID-19 cases deceased by age group in Canada as of January 21, 2023
odCovid.by.age <- COpenData$new(
  myname = "odCovid.by.age",
  info =  c (source = "PHAC Epi Update:  Covid Cases/Deaths",
             title = "By age and gender, relative to population size, all provinces combined",
             title.short = "COVID-19 Deaths -- by age and gender",
             url  = "https://health-infobase.canada.ca/covid-19",
             comment = "Figure 3. Weekly number of COVID-19 cases deceased by age group in Canada as of January 21, 2023"), 
  csv =  c(live="https://health-infobase.canada.ca/src/data/covidLive/covid19-epiSummary-ageGender.csv",
           local = "covid19-epiSummary-ageGender.csv"
  )
)

self <- odCovid.by.province
# self <- odCovid.by.age

if (F) { # C_OPEN_DATA_USE_STORED_CLASSES) {
  self <- self$restore.me()
} 
if (T) { # read and store.me()
  if (T) { # C_OPEN_DATA_USE_LOCAL) {
    self$fread.csv("local")
  } else {
    self$fread.csv("live")
    if (F) {
      self$fwrite.csv(timestamp = T);   self$fwrite.csv(timestamp = F)
    }
  }
  opendata.view(self)
}
if (T) {
  odCovid.by.province$fLte.Define(
    function (self) {
      # Add / remove columns / Compute additional metrics
      self$dt[, population:= round(numdeaths/ratedeaths * 100000, -3)] 
      self$dt %>% dt.select (c("date", "prname", "numdeaths_last7", "ratedeaths_last7", "population"))
      #  filter (selecte by) rows
      self$dt <- self$dt [prname!="Repatriated travellers"]
      # rename columns
      setnames(self$dt, "date", "Date") 
      setnames(self$dt, "prname", "GEO") 
      dt.clean.geo.canada(self$dt, "GEO")
      # self$setDate("date")
      # self$setGeo("prname")
      
      self$setFactors(c("GEO"))
      
      # what are factors
      self$col.factors <- c("GEO")

      # what are metrics
      self$col.metrics <- c("numdeaths_last7", "ratedeaths_last7", "population")

      # self$dt <- self$dt %>% melt(1:2, variable.factor = T) # warnings are ok here
      # 
      # self$col.factors <- c("GEO", "variable")
      # self$col.value = "value"
      # # self$dt[is.na(value), value := 0]
      # self$dt %>% setorder(-Date) 
    }
  )
  self$fLte(self)
}

opendata.view(self)
self$dt[!is.na(get(self$col.metrics[1])), .SD[.N], by=mget(self$col.factors)] 
self$input
self$get.dt()
self$get.dt.subset()
self$get.dt.melted()
self$get.dt.melted(subset = T)
self$get.dt.summary()
self$get.dt.summary(subset = T)


self$get.dt()
self$get.dt.subset() %>% 

self$get.dt() %>% datatable.title() 
self$get.dt.subset() %>% datatable.title() 
self$get.dt.subset() %>% dt2dt.with.date.as.character %>% datatable.title() 



if (T){
  self$store.me()
}
odCovid.by.province <- self$clone()

r$cWin1 <- self$clone()

self$input$grid.melted = T
self$input$grid.summary = T
opendata.grid (self)

opendata.plot (self)

################################################### #



odCovid.by.age$fLte.Define(
  function (self) {
    self$dt[, population:=round(count/rate_per_100000 * 100000, -3)]
    self$dt[, `Weekly (13W SMA)`:= as.integer(frollmean(count, 4, align = "left", fill = 0)), by = cCovid.by.age$dtfactors]
    
    self$dt <- self$dt %>% melt(c(1:4), variable.factor = T) # warnings are ok here
    
    self$col.factors <- self$dt %>% names() %>%  .[2:5];  self$col.factors
    self$col.value =  self$dt %>% names() %>% .[6]; self$col.value # "value"
    # self$dt[is.na(value), value := 0]
    
    # self$dt <- self$dt [status == "deaths"]
    self$setDate("date")
  }
)


```


## *** 1. PHAC Epi Update:  Covid Cases/Deaths *** {.tabset .tabset-fade}
### COVID-19 Deaths - by province

```{r}

```

> Deaths by province, relative to population size, all ages combined. 
csv: <https://health-infobase.canada.ca/src/data/covidLive/covid19-download.csv> (linked at <https://health-infobase.canada.ca/covid-19>)"



###  COVID-19 Deaths - by age and gender

<!-- , relative to population size, all provinces combined (Canada) -->



```{r}

# dt [Sex =="Both sexes"] %>%   ggplot() +     guides(x =  guide_axis(angle = 60))  +
#   geom_line(aes(x=Date, y=rate_per_100000      , col=Sex) )+
#   facet_grid( Age ~ Sex, scales = "free")


q ="Sex==Sex"
# q = qoute (Sex =="Both sexes")
q = ' Sex =="Both sexes" '

g <- cCovid.by.age$dt [eval(parse(text=q))]  %>%   ggplot() +     
  guides(x =  guide_axis(angle = 60))  +
  theme(legend.position = "bottom")  +
  geom_line(aes(x=Date, y=`Weekly (13W SMA)`), col="red" )+
  facet_grid( . ~ Age, scales = "fixed") +
  
  labs( title = "COVID-19 Cases deceased, by age group. All sexes and all provinces combined",
        # subtitle = "All sexes and all provinces combined",
        caption = paste0 ("Source: https://health-infobase.canada.ca/src/data/covidLive/covid19-epiSummary-ageGender.csv",
                          "\nGenerated by OpenCanada.info Tracker on ", dateToday),
        
        x=NULL, col=NULL
  )

# g.add.pandemic <- function(g) {
alp = 0.3
for (i in 1:length(period)) {
  g <- g + geom_vline(xintercept=period[i], linetype=5, alpha=alp,  col="darkgrey", size=1)
}
# g <- g + xlim(input$date[1], input$date[2])
g <- g + geom_vline(xintercept=period[1], linetype=1, alpha=alp,  col="darkgrey", size=4)

# }

# g <- g + g.add.pandemic(g)
g

```

> Source: https://health-infobase.canada.ca/src/data/covidLive/covid19-epiSummary-ageGender.csv


### Population 

```{r}


g <- cCovid.by.age$dt  %>%   ggplot() +     
  guides(x =  guide_axis(angle = 60))  +
  theme(legend.position = "bottom")  +
  geom_line(aes(x=Date, y=population), col="red" )+
  facet_grid( Sex ~ Age, scales = "fixed") +
  
  labs( title = "COVID-19 Cases deceased, by age group. All sexes and all provinces combined",
        # subtitle = "All sexes and all provinces combined",
        caption = paste0 ("Source: https://health-infobase.canada.ca/src/data/covidLive/covid19-epiSummary-ageGender.csv",
                          "\nGenerated by OpenCanada.info Tracker on ", dateToday),
        
        x=NULL, col=NULL
  )

# g.add.pandemic <- function(g) {
alp = 0.3
for (i in 1:length(period)) {
  g <- g + geom_vline(xintercept=period[i], linetype=5, alpha=alp,  col="darkgrey", size=1)
}
# g <- g + xlim(input$date[1], input$date[2])
g <- g + geom_vline(xintercept=period[1], linetype=1, alpha=alp,  col="darkgrey", size=4)

# }

# g <- g + g.add.pandemic(g)
g

```



# COVID-19 Vaccination coverage & Population - by age, gender, province {data-orientation=rows, data-navmenu="PHAC"}



##  2: *** Vaccination + population,  ***


<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- ### By province - all ages - NO dose information ! -->


<!-- h3("By province - all ages - NO dose information !") -->


<!-- ################################################################ #  -->
<!-- # https://health-infobase.canada.ca/covid-19/vaccination-coverage/ ##### -->
<!-- ################################################################ #  -->

<!-- # Figure 1 -->
<!-- url <- "https://health-infobase.canada.ca/src/data/covidLive/vaccination-coverage-map.csv" -->
<!-- dtv1  <- fread(url) -->


<!-- # Figure 5 -->
<!-- url <- "https://health-infobase.canada.ca/src/data/covidLive/vaccination-coverage-byVaccineType.csv" -->
<!-- dtv3  <- fread(url) -->

<!-- ``` -->

<!-- >  -->
<!-- Source: Public Health Agency of Canada - [COVID-19 vaccination in Canada](https://health-infobase.canada.ca/covid-19/vaccination-coverage/) -->



### Vaccine administration - by province, dose, age, gender

```{r include=FALSE}

# Figure 3
cVaccines <- COpenData$new(
  title = "Vaccine administration - by province, dose, age, gender",
  csv =  "https://health-infobase.canada.ca/src/data/covidLive/vaccination-coverage-byAgeAndSex-overTimeDownload.csv",
  url  = "https://health-infobase.canada.ca/covid-19",
  csv.local = "vaccination-coverage-byAgeAndSex-overTimeDownload.csv",
  comments.priv="Changed between 2023-02-03 and 2023-02-11"
)

cVaccines$fread.csv("local")
# cVaccines$fread.csv("live")
if (F) {
  cVaccines$fwrite.csv(timestamp=F, tozip=F, tords=F)
}

# 

cVaccines$..v()
cVaccines$dt$prfname   <- cVaccines$dt$pruid <- NULL

cVaccines$dt$age %>% u
cVaccines$dt$sex %>% u



cVaccines$dt %>% 
  setnames("prename", "GEO") %>% 
  setnames( "week_end", "Date") %>% 
  setcolorder("Date")

cols <-  cVaccines$dt %>% names %wo% c("GEO"  , "Date"  ,  "sex"   , "age" );cols
cVaccines$dt [, (cols):= lapply(.SD, as.numeric), .SDcols = cols]


setcolorder("Date", "GEO", )

cVaccines$dt [,  population := round( numtotal_atleast1dose / proptotal_atleast1dose  * 100, -2)  ]



cVaccines$dt %>% melt(id=1:3, measure=patterns(numbertotal="numtotal_", proptotal="proptotal_"))

cVaccines$dt %>% melt(id=1:3, measure=patterns(numbertotal="numtotal_"))


cVaccines$dt <- cVaccines$dt[sex=="All sexes"]
cVaccines$dt$sex <- NULL
# cVaccines$dt <- cVaccines$dt[ age %ni% c("Not reported", "Unknown", "0–15", "16–69","70–74" , "75–79", "18–69","0–17" )]

cVaccines$factors <- c("GEO", "age") # "sex" 




cols.weekly <- paste0(cols, ".weekly")

cVaccines$dt [, (cols):= lapply(.SD, as.numeric), .SDcols = cols]

# to do shift
setorder(cVaccines$dt, Date      )
cVaccines$dt [, (cols.weekly):= lapply(.SD, function(x) {x-shift(x,1) }), .SDcols = cols, by=cVaccines$factors ]
setorder(cVaccines$dt, - Date )# setorder(dt, - week_end ) # for viewing 


cols.metrics.num <- c(   "numtotal_atleast1dose" ,  "numtotal_partially"   , "numtotal_fully"   ,   "numtotal_additional" , "numtotal_2nd_additional" , "numtotal_recent_fullyoradditional"   )
cols.metrics<- c(   "total_atleast1dose" ,  "total_partially"   , "total_fully"   ,   "total_additional" , "total_2nd_additional" , "total_recent_fullyoradditional"   )
cols.metrics.prop <-  paste0("prop",cols.metrics)
cols.metrics.num.weekly <- paste0(cols.metrics.num, ".weekly")
cols.metrics.prop.weekly <- paste0(cols.metrics.prop, ".weekly")

str_replace(cols.metrics.num, "numtotal_", "")

for (i in 1:length(cols.metrics)) {
  col.prop.weekly=cols.metrics.prop.weekly[i]
  col.weekly=cols.metrics.prop.weekly[i]
  
}
# dt[, (cols.metrics.prop.weekly):= lapply(.SD, function(x) {x/population} ), cols.metrics.num.weekly]



if (T) {
  dtPop = cVaccines$dt [, .(population = round( numtotal_atleast1dose / proptotal_atleast1dose  * 100, -2) ), by=c("Date", cVaccines$factors) ]
  
  # cVaccines$dt$opulation = cVaccines$dt$numtotal_atleast1dose / cVaccines$dt$numtotal_atleast1dose * 100
  # cVaccines$dt [,  population := round( numtotal_atleast1dose / proptotal_atleast1dose  * 100, -2)  ]
  
  if (F) {
    dtPop [prename== "Canada" & !is.na(population) & 
             # sex=="f" & 
             age=="12–17"
    ] [1:3] # population adds up !
    
    dtPop [prename== "Canada" & !is.na(population)   ] [1:11] # population adds up ? does not have 80+
    dtPop [prename== "Alberta" & !is.na(population)   ] [1:11] # population adds up ? does not have 80+
    dtPop [prename== "Ontario" & !is.na(population)   ] [1:11] # population adds up ! 80+
    
    dtPop$sex %>% u
    dtPop$age %>% u
    
    dt [prename== "Canada"]
  }
  
  
}


if (F) {
  metric <- "Unnamed: 22" # WHAT ARE THESE??? These are POPULATION for all 7 days of reporting week
  metric.num <- metric 
  dt[prename== "Canada" & !is.na(`Unnamed: 22`)]$`Unnamed: 22`
  
  dt[!is.na(`Unnamed: 22`)]  %>%   ggplot(aes(x=week_end)) +     
    guides(x =  guide_axis(angle = 60))  +
    scale_x_date(date_labels = "%b %Y", date_breaks = "3 months") +
    facet_grid( prename ~ age, scale="free_y" ) + # ylim(0, NA) +
    geom_point(aes(y=`Unnamed: 22`, size=3), ) + labs(y=metric, x=NULL)
  
  dt[, .SD[1], by= prename ] %>% datatable.title()
  
}

period = c(
  # ymd("2010-01-05"), # early prepandemic, early flu waves 
  # ymd("2020-01-01"), # four new cause categories added: 3 for covid + NO_INFO
  ymd("2021-12-01"), # 
  # ymd("2022-01-01"), 
  ymd("2022-03-01") # # 
)


# PLOTTIN ------

if (F) {
  ######################################### #
  
  i=1
  for (i in 1:length(cols.metrics)) { 
    
    metric <- cols.metrics[i];metric
    # metric.num <- cols.metrics.num [i]
    # metric.prop <- cols.metrics.prop [i]
    metric.weekly <- cols.metrics.num.weekly [i] 
    metric.title <- str_replace(metric, "total_", "")
    
    
    g <- cVaccines$dt  %>%   ggplot(aes(x=Date)) +     
      guides(x =  guide_axis(angle = 60))  +
      facet_grid( GEO ~ age, scale="free_y" ) +  ylim(0, NA) +
      
      
      labs(y="Doses administered weekly", 
           x=NULL,          title = metric.title,
           caption=paste("Generated by OpenCanada.info tracker on", dateToday)
      )
    
    if (T) { # input$vline) {
      alp = 0.5
      for (iii in 1:length(period)) {
        g <- g + geom_vline(xintercept=period[iii], linetype=5, aplha=alp,  col="grey")
      }
      # g <- g + xlim(input$date[1], input$date[2])
    }
    
    
    g <- g + geom_line(aes(y=get(metric.weekly)) ) # , col=i, linetype=i) 
    
    ggsave(paste("png/", dateToday,"-", i, "-", metric.title, ".png"), width=12, height=9)
    
    print(i)
    print(metric); 
    
  }
  
  print(g)
  
}

```



# COVID-19 Vaccince safety - by age {data-orientation=rows, data-navmenu="PHAC"}

## 3: Vaccince safety ----

```{r eval=FALSE, include=FALSE}



################################################################ # 
# https://health-infobase.canada.ca/covid-19/vaccine-safety/
############################################################### ## 


url <- "https://github.com/opencanada-info/phac-covid-vaccine-safety/raw/main/side-effects-2023-01-20.csv"
dt <- fread(url, skip=5)
saveRDS(dt, 'phac-safety-till-2023-01-06) # accessed 11 feb 2023




```


```{r eval=FALSE, include=FALSE}



self$view.Define( 
  function (self=self, show="summary") { # cat screwed the dates! better touse glue (.{})
    # cat(
    #   "Title: ", self$info[["title"]],
    #   "\n From ", self$dateMin %>% as.character() ,
    #   "to",   self$dateMin %>% as.character(), "\n"
    # ) %>% print
    
    self$dt %>% names %>% print
    self$dt %>% dim %>% print
    self$dt[c(1, .N)] %>% print
    # if (show == "summary")
    #   self$dt %>% dt.get.summary(self$col.factors) %>% print
    
    cat("Subset:\n " )
    self$dt0 %>% dim %>% print
    self$dt0[c(1, .N)] %>% print
    
    # if (show == "summary")
    #   self$dt0 %>% dt.get.summary(self$col.factors) %>% print
    # self$dt %>% .[GEO=="Alberta"] %>% print
  }
)



```

