---
title: "OpenCanada.info: Statistics Canada"
output: flexdashboard::flex_dashboard
runtime: shiny
---



```{r global, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
source("lib_opendata.R")
```


# Data sources

## 

###

Statistics Quebec updated the excess deaths (surmortalité in French) per age group at the beginning of May. 

Surmortalité hebdomadaire selon le groupe d'âge, Québec, 2020‑2023

https://statistique.quebec.ca/fr/document/surmortalite-hebdomadaire/publication/surmortalite-hebdomadaire-selon-groupe-dage-quebec

The raw numbers of total deaths per week were also updated, and 2022 does not look good at all: worse than 2021 and 2020 (minus the cluster of deaths during the first lockdown, of course).


https://statistique.quebec.ca/fr/document/surmortalite-hebdomadaire/publication/surmortalite-hebdomadaire-quebec-et-certaines-regions-du-canada


https://statistique.quebec.ca/fr/document/nombre-hebdomadaire-de-deces-au-quebec/publication/deces-par-semaine-selon-groupe-age-quebec

-> 

https://statistique.quebec.ca/fr/document/nombre-hebdomadaire-de-deces-au-quebec/publication/nombre-hebdomadaire-de-deces-au-quebec-source-de-donnees-et-methodologie

Nombre hebdomadaire de décès au Québec, 2010-2023
https://statistique.quebec.ca/fr/document/nombre-hebdomadaire-de-deces-au-quebec


### Décès par semaine selon le groupe d'âge, Québec, 2010-2023
https://statistique.quebec.ca/fr/document/nombre-hebdomadaire-de-deces-au-quebec/tableau/deces-par-semaine-selon-le-groupe-dage-quebec#tri_gp=950



Lien permanent du tableau
statistique.quebec.ca/fr/produit/tableau/3936 = https://statistique.quebec.ca/en/produit/tableau/3936#tri_gp=950
Total

0-49 ans
https://statistique.quebec.ca/fr/produit/tableau/3936#tri_gp=28
50-59
https://statistique.quebec.ca/fr/produit/tableau/3936#tri_gp=605
60-69
https://statistique.quebec.ca/fr/produit/tableau/3936#tri_gp=690
70-79
https://statistique.quebec.ca/fr/produit/tableau/3936#tri_gp=788

80-89
https://statistique.quebec.ca/fr/produit/tableau/3936#tri_gp=863
90 ans et plus
https://statistique.quebec.ca/fr/produit/tableau/3936#tri_gp=925


https://statistique.quebec.ca/docs-ken/multimedia/DecesSemaine_QC_GrAge.xlsx

```{r}
self$dt <- readxl::read_excel(self$data[[origin]], sheet = self$data[[xls.sheet]])



self <- COpenData$new(
  myname="odQB.deaths.by.age",
  info=c(
    title = "Weekly deaths by age group, Québec",
    webpage = NA,
    comment=NA
  ),
  data = c (
    origin="xls",
    xls = "https://statistique.quebec.ca/docs-ken/multimedia/DecesSemaine_QC_GrAge.xlsx",
    xls.sheet =1
    
  )
)

self$dt <- readxl::read_excel(self$data[["xls"]], sheet = self$data[["xls.sheet"]])
self$dt <- openxlsx::read.xlsx(self$data[["xls"]], sheet = 1, skipEmptyRows=F, startRow=6)
# dt2 <- openxlsx::read.xlsx(self$data[["xls"]], sheet=2)

self$dt %>% setDT

self$dt <- self$dt %>% melt (1:3)
self$dt [, value:=as.integer(value)]
self$dt [, variable :=as.character(variable )]
self$dt$Statut <- NULL
self$dt %>% setnames(names(self$dt ), c("yy", "age", "ww", "deaths"))
self$dt[ , newyears := ymd(paste0(yy,"-01-01") )] [, Date:= newyears + weeks(as.integer(ww)-1)] [, newyears:=NULL][]

```

### Naissances, décès et mariages par mois et par trimestre, Québec, 1995-2023

https://statistique.quebec.ca/fr/produit/tableau/naissances-deces-et-mariages-par-mois-et-par-trimestre-quebec#tri_phe=3528

https://statistique.quebec.ca/fr/produit/tableau/698
décès 
https://statistique.quebec.ca/fr/produit/tableau/698#tri_phe=3528
Naissances
https://statistique.quebec.ca/fr/produit/tableau/698#tri_phe=3527
