---
title: "OpenCanada.info: PHAC"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r  include=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE)
source("opencanada-base.R")
```

# COVID-19 Deaths -- by gender and province {data-orientation=columns, data-navmenu="PHAC"}

<!-- ## Settings: {.sidebar} -->

 "Rates of COVID-19 Cases and Deaths by Vaccination Status",
https://covid.cdc.gov/covid-data-tracker/#rates-by-vaccine-status 

leads to data:

Data for CDC’s COVID Data Tracker site on Rates of COVID-19 Cases and Deaths by Updated (Bivalent) Booster Status:
https://data.cdc.gov/Public-Health-Surveillance/Rates-of-COVID-19-Cases-or-Deaths-by-Age-Group-and/54ys-qyzm

leads to API:

Access this Dataset via SODA API

The Socrata Open Data API (SODA) provides programmatic access to this dataset including the ability to filter, query, and aggregate data.

https://data.cdc.gov/resource/54ys-qyzm.json


Archive: 

An archive of historic data, including April 3, 2021-September 24, 2022 and posted on October 21, 2022 is available on data.cdc.gov. 

The analysis by vaccination status (unvaccinated and at least a primary series) for 31 jurisdictions is posted here: https://data.cdc.gov/Public-Health-Surveillance/Rates-of-COVID-19-Cases-or-Deaths-by-Age-Group-and/3rge-nu2a. 

The analysis for one booster dose (unvaccinated, primary series only, and at least one booster dose) in 31 jurisdictions is posted here: https://data.cdc.gov/Public-Health-Surveillance/Rates-of-COVID-19-Cases-or-Deaths-by-Age-Group-and/d6p8-wqjm. 

The analysis for two booster doses (unvaccinated, primary series only, one booster dose, and at least two booster doses) in 28 jurisdictions is posted here: https://data.cdc.gov/Public-Health-Surveillance/Rates-of-COVID-19-Cases-or-Deaths-by-Age-Group-and/ukww-au2k.



```{r}

local = "cdc-rates-by-vaccine-status.csv"

library(RSocrata)

dt <- read.socrata("https://data.cdc.gov/resource/54ys-qyzm.json")
dt %>% setDT

allSitesDataFrame <- ls.socrata("https://soda.demo.socrata.com")
allSitesDataFrame$title

odUS.by.vax <- COpenData$new(
  myname = "odUS.by.vax",
  info =  c (
    source = "CDC",
    title.short = "Rates of COVID-19 Cases and Deaths by Vaccination Status",
    title="Rates of COVID-19 Cases or Deaths by Age Group and Updated (Bivalent) Booster Status",
    comment ="",
    Webpage  = "https://covid.cdc.gov/covid-data-tracker/#rates-by-vaccine-status",
    data="https://data.cdc.gov/Public-Health-Surveillance/Rates-of-COVID-19-Cases-or-Deaths-by-Age-Group-and/54ys-qyzm"
    ),
  data = c(
    socrata = "https://data.cityofchicago.org/resource/f7f2-ggz5.json",
    csv.cached=".\\github_opencanada-info\\World\\us\\Rates_of_COVID-19_Cases_or_Deaths_by_Age_Group_and_Updated__Bivalent__Booster_Status.csv",
    csv.local = "cdc-rates-by-vaccine-status.csv"
  )
)
self <- odUS.by.vax

self %>% od.fread("csv.cached")
self %>% od.view

self %>% od.fwrite(timestamp = T);   
self %>% od.fwrite(timestamp = F)

self$dt[ , Date:= as.Date(paste(mmwr_week,1),"%Y%U %u") ]

self$dt <- self$dt [outcome     == "death"]

self$dt %>% dt.remove(c( "outcome", "month", "mmwr_week"        ))
self$dt %>% setcolorder("Date")

self$dt %>%  melt (id=1:7, 
              measure.vars= patterns(crude="^crude_", age_adj="^age_adj_", monthly_age_adj="^monthly_age_adj_"), value.factor = T )



g <- self %>% od.plot.layout +
    geom_point(aes (y=vaccinated_with_outcome, col=vaccination_status  )) + 
  geom_line(aes (y=unvaccinated_with_outcome  )) + 
  facet_grid(age_group ~ ., scales = "free")
g
g+gg
  

g <-  self$dt %>%     
  ggplot() +
  # geom_line(aes (mmwr_week , vaccinated_with_outcome, col=vaccination_status  )) + 
  geom_line(aes (Date , unvaccinated_with_outcome  )) +
  facet_grid(age_group ~ continuity_correction, scales = "free");g


g <-  self$dt %>%     
  ggplot() +
  geom_point(aes (Date , vaccinated_with_outcome, col=vaccination_status  )) + 
  geom_point(aes (Date , unvaccinated_with_outcome  )) + 
  facet_grid(age_group ~ continuity_correction, scales = "free")
g

g <-  self$dt %>%     
  ggplot() +
  geom_point(aes (Date , crude_vax_ir , col=vaccination_status  )) + 
  geom_point(aes (Date , crude_unvax_ir     )) + 
  geom_point(aes (Date , crude_irr      ), shape=2) + 
  facet_grid(age_group ~ ., scales = "free")
g



## TEST ZONE ----- 

# https://stackoverflow.com/questions/75678367/melt-data-table-using-patterns-with-automated-extraction-of-measure-names

DT <- data.table(
    parent.name = words[101:103],
    parent.dob = as.Date(1:3, origin="2020-01-01"),
    child_boy = words[11:13],
    child_girl = words[21:23],
    child_trans = words[201:203],
    dob_boy= as.Date(1:3, origin="2010-01-01"),
    dob_girk= as.Date(1:3, origin="2012-01-01"), 
    dob_trans= as.Date(1:3, origin="2022-01-01") 
  )
  DT

  DT2 <- melt(DT, id.vars = c("parent.name", "parent.dob"),   measure=patterns(dob="^dob_", name="^child_"), value.factor=TRUE, variable.name =  "child")
  DT2
  DT2 [child=="1", child:="boy"] [child=="2", child:="girl"][child=="3", child:="trans"]
 DT2

 
x <- melt(DT, id.vars = c("parent.name", "parent.dob"))
x[, c("variable", "name") := tstrsplit(variable, "_", fixed = TRUE)]
dcast(x, parent.name + parent.dob + name ~ variable)





tidyr::pivot_longer(DT, -(1:2),
  names_pattern = "(.*)_(.*)", names_to = c(".value", "name"))


```